---
title: "Trains"
author: "Leo Katz"
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(gt)
```

```{r}
#| include: false
glimpse(trains)
```

```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |> 
  fit(att_end ~ treatment, data = trains)
```

```{r}
tidy(fit_att, conf.int = TRUE)
```

```{r}
# Create a formatted table of the model results
tidy(fit_att, conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  gt() %>%
  tab_header(
    title = "Immigration Attitude Model Estimates",
    subtitle = "Data Source: trains experiment from primer.data"
  ) %>%
  cols_label(
    term = "Term",
    estimate = "Estimate",
    conf.low = "Lower 95% CI",
    conf.high = "Upper 95% CI"
  ) %>%
  fmt_number(
    columns = c(estimate, conf.low, conf.high),
    n_sigfig = 3
  )
```

## Summary

Attitudes toward immigration are related to brief encounters with speakers of another language in daily life, at least somewhat. Using data from Ryan Enos’s January 2012 randomized experiment on Boston-area Metra platforms (115 commuters, randomly assigned to exposure or non-exposure to Spanish-speaking confederates for two weeks), we estimate the average causal effect of that exposure on anti-immigration attitudes.However, the small dataset we have is not fully representative of the entire population, including the Georgia voters our canidate cares about, so deviation from the model is predicted. We model immigration attitudes as a linear function of exposure to Spanish-speakers.

